Output Summary

### 2021-08-04 03-post-process/output-plots.Rmd
Add aggregated composition plots to output-plots
Can help diagnose lack of fit issues with respect to age, sex, or origin specifically

# read information from this model
model_info = readRDS(file.path(in_dir, paste0(params$pop, "output-", params$scenario, ".rds")))

# extract the two key structures from this object
post = model_info$post
jags_data = model_info$jags_data

@@

# dimension IDs
i_fall   = 1  # fall migrants are i = 1
i_spring = 2  # spring migrants are i = 2,
o_nor    = 1  # natural origin are o = 1,
o_hor    = 2  # hatchery origin are o = 2,
s_female = 1  # females are s = 1,
s_male   = 2  # males are s = 2
j_cat    = 1  # Catherine Creek is j = 1
j_los    = 2  # Lostine River is j = 2
j_min    = 3  # Minam River is j = 3
j_ugr    = 4  # Upper Grande Ronde River is j = 4
k_3      = 1  # age 3 is k = 1
k_4      = 2  # age 4 is k = 2
k_5      = 3  # age 5 is k = 3
```

The code used to render this output relies heavily on Staton's 'postpack' package (now available on CRAN). Take a look at [this vignette](https://bstaton1.github.io/postpack/articles/feature-overview.html) for a primer on how to use it.

@@

@@

```{r weir-comp-fit-func}
weir_comp_fit_plot = function(j) {
  # calculate observed q
  q_obs = t(apply(jags_data$weir_x_obs[,,j], 1, function(y) y/sum(y)))

@@

  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
```

#### CAT

```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(1)
```

#### LOS

```{r lost-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(2)
```

#### MIN

```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(3)
```

#### UGR

```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(4)
```

@@

```{r carc-comp-fit-func}
carc_comp_fit_plot = function(j) {

@@

  par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,7,pop]$", pop = j)), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,8,pop]$", pop = j)), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,9,pop]$", pop = j)), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,10,pop]$",pop = j)), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,11,pop]$",pop = j)), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,12,pop]$",pop = j)), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
}
```

#### CAT

```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(1)
```

#### LOS

```{r lost-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(2)
```

#### MIN

```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(3)
```

#### UGR

```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(4)
```

>>>>

# read information from this model
model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))

# extract the two key structures from this object
post = model_info$post
# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data

@@

# dimension IDs
i_fall   = 1  # fall migrants are i = 1
i_spring = 2  # spring migrants are i = 2,
o_nor    = 1  # natural origin are o = 1,
o_hor    = 2  # hatchery origin are o = 2,
s_female = 1  # females are s = 1,
s_male   = 2  # males are s = 2
j_cat    = 1  # Catherine Creek is j = 1
j_los    = 2  # Lostine River is j = 2
j_min    = 3  # Minam River is j = 3
j_ugr    = 4  # Upper Grande Ronde River is j = 4
k_3      = 1  # age 3 is k = 1
k_4      = 2  # age 4 is k = 2
k_5      = 3  # age 5 is k = 3

# kso represents "age/sex/origin" combo
# e.g., kso = 1 is age 3 female NORs
# e.g., kso = 12 is age 5 male HORs
# these objects specify which elements of kso are for different aggregations of these
kso_age = list(
  kso_3 = c(1, 4, 7, 10),
  kso_4 = c(2, 5, 8, 11),
  kso_5 = c(3, 6, 9, 12)
)

kso_sex = list(
  kso_female = c(1,2,3,7,8,9),
  kso_male = c(4,5,6,10,11,12)
)

kso_origin = list(
  kso_nor = 1:6,
  kso_hor = 7:12
)
```

@@

```{r calculate-aggregated-comps-model}
# extract the full posteriors of the two composition sets
q_Ra_full = post_subset(post, "q_Ra", matrix = TRUE)
q_Sa_adj_full = post_subset(post, "q_Sa", matrix = TRUE)

# primary containers: will store final recalculated output
q_Ra_age = q_Sa_adj_age = q_Ra_sex = q_Sa_adj_sex = q_Ra_origin = q_Sa_adj_origin = NULL

# number of posterior samples
n = post_dim(post, "saved")

# loop through posterior samples, calculate various aggregates of composition by type
for (i in 1:n) {

  # format the posterior draw as arrays -- easier to subset
  q_Ra = array_format(q_Ra_full[i,])
  q_Sa_adj = array_format(q_Sa_adj_full[i,])

  ## BY AGE, AGGREGATED ACROSS SEX AND ORIGIN

  # containers
  q_Ra_age_tmp = q_Sa_adj_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
  inds_1_age = inds_2_age = inds_3_age = q_Ra_age_tmp
  for (j in 1:jags_data$nj) {
    for (k in 1:jags_data$nk) {
      # calculate aggregate proportions for each age
      q_Ra_age_tmp[,k,j] = rowSums(q_Ra[,kso_age[[k]],j])
      q_Sa_adj_age_tmp[,k,j] = rowSums(q_Sa_adj[,kso_age[[k]],j])

      # build the element identifiers - for building names later
      inds_1_age[,k,j] = 1:jags_data$ny
      inds_2_age[,k,j] = k
      inds_3_age[,k,j] = j
    }
  }

  # vectorize, add names, and remove NAs
  q_Ra_age_v = as.numeric(q_Ra_age_tmp)
  q_Sa_adj_age_v = as.numeric(q_Sa_adj_age_tmp)
  names(q_Ra_age_v) = paste0("q_Ra_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  names(q_Sa_adj_age_v) = paste0("q_Sa_adj_age[", as.numeric(inds_1_age), ",", as.numeric(inds_2_age), ",", as.numeric(inds_3_age), "]")
  q_Ra_age_v = q_Ra_age_v[!is.na(q_Ra_age_v)]
  q_Sa_adj_age_v = q_Sa_adj_age_v[!is.na(q_Sa_adj_age_v)]

  ## BY SEX, AGGREGATED ACROSS AGE AND ORIGIN

  # containers
  q_Ra_sex_tmp = q_Sa_adj_sex_tmp = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
  inds_1_sex = inds_2_sex = inds_3_sex = q_Ra_sex_tmp
  for (j in 1:jags_data$nj) {
    for (s in 1:jags_data$ns) {
      # calculate aggregate proportions for each sex
      q_Ra_sex_tmp[,s,j] = rowSums(q_Ra[,kso_sex[[s]],j])
      q_Sa_adj_sex_tmp[,s,j] = rowSums(q_Sa_adj[,kso_sex[[s]],j])

      # build the element identifiers - for building names later
      inds_1_sex[,s,j] = 1:jags_data$ny
      inds_2_sex[,s,j] = s
      inds_3_sex[,s,j] = j
    }
  }

  # vectorize, add names, and remove NAs
  q_Ra_sex_v = as.numeric(q_Ra_sex_tmp)
  q_Sa_adj_sex_v = as.numeric(q_Sa_adj_sex_tmp)
  names(q_Ra_sex_v) = paste0("q_Ra_sex[", as.numeric(inds_1_sex), ",", as.numeric(inds_2_sex), ",", as.numeric(inds_3_sex), "]")
  names(q_Sa_adj_sex_v) = paste0("q_Sa_adj_sex[", as.numeric(inds_1_sex), ",", as.numeric(inds_2_sex), ",", as.numeric(inds_3_sex), "]")
  q_Ra_sex_v = q_Ra_sex_v[!is.na(q_Ra_sex_v)]
  q_Sa_adj_sex_v = q_Sa_adj_sex_v[!is.na(q_Sa_adj_sex_v)]

  ## BY ORIGIN, AGGREGATED ACROSS AGE AND SEX

  # containers
  q_Ra_origin_tmp = q_Sa_adj_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
  inds_1_origin = inds_2_origin = inds_3_origin = q_Ra_origin_tmp
  for (j in 1:jags_data$nj) {
    for (o in 1:jags_data$no) {
      # calculate aggregate proportions for each origin
      q_Ra_origin_tmp[,o,j] = rowSums(q_Ra[,kso_origin[[o]],j])
      q_Sa_adj_origin_tmp[,o,j] = rowSums(q_Sa_adj[,kso_origin[[o]],j])

      # build the element identifiers - for building names later
      inds_1_origin[,o,j] = 1:jags_data$ny
      inds_2_origin[,o,j] = o
      inds_3_origin[,o,j] = j
    }
  }

  # vectorize, add names, and remove NAs
  q_Ra_origin_v = as.numeric(q_Ra_origin_tmp)
  q_Sa_adj_origin_v = as.numeric(q_Sa_adj_origin_tmp)
  names(q_Ra_origin_v) = paste0("q_Ra_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
  names(q_Sa_adj_origin_v) = paste0("q_Sa_adj_origin[", as.numeric(inds_1_origin), ",", as.numeric(inds_2_origin), ",", as.numeric(inds_3_origin), "]")
  q_Ra_origin_v = q_Ra_origin_v[!is.na(q_Ra_origin_v)]
  q_Sa_adj_origin_v = q_Sa_adj_origin_v[!is.na(q_Sa_adj_origin_v)]

  ## COMBINE NEW CALCULATED QUANTITIES ACROSS POSTERIOR SAMPLES

  q_Ra_age = rbind(q_Ra_age, q_Ra_age_v)
  q_Sa_adj_age = rbind(q_Sa_adj_age, q_Sa_adj_age_v)
  q_Ra_sex = rbind(q_Ra_sex, q_Ra_sex_v)
  q_Sa_adj_sex = rbind(q_Sa_adj_sex, q_Sa_adj_sex_v)
  q_Ra_origin = rbind(q_Ra_origin, q_Ra_origin_v)
  q_Sa_adj_origin = rbind(q_Sa_adj_origin, q_Sa_adj_origin_v)

# combine new calculated quantites into a big matrix
q_new = cbind(q_Ra_age, q_Sa_adj_age, q_Ra_sex, q_Sa_adj_sex, q_Ra_origin, q_Sa_adj_origin)

# combine with the rest of the posterior samples
post = post_bind(post, q_new)

```{r calculate-aggregated-comps-data}

# these are the observed proportions by age (aggregated across sex and origin), sex (aggregated across age and origin), and origin (aggregated across age and sex)

# containers
q_weir_age_obs = q_carc_age_obs = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
q_weir_sex_obs = q_carc_sex_obs = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
q_weir_origin_obs = q_carc_origin_obs = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))

for (j in 1:jags_data$nj) {
  # calculate aggregate proportions for each age
  for (k in 1:jags_data$nk) {
    q_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,kso_age[[k]],j])/jags_data$weir_nx_obs[,j]
    q_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,kso_age[[k]],j])/jags_data$carc_nx_obs[,j]
  }

  # calculate aggregate proportions for each sex
  for (s in 1:jags_data$ns) {
    q_weir_sex_obs[,s,j] = rowSums(jags_data$weir_x_obs[,kso_sex[[s]],j])/jags_data$weir_nx_obs[,j]
    q_carc_sex_obs[,s,j] = rowSums(jags_data$carc_x_obs[,kso_sex[[s]],j])/jags_data$carc_nx_obs[,j]
  }

  # calculate aggregate proportions for each origin
  for (o in 1:jags_data$no) {
    q_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,kso_origin[[o]],j])/jags_data$weir_nx_obs[,j]
    q_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,kso_origin[[o]],j])/jags_data$carc_nx_obs[,j]
  }
}

dimnames(q_weir_age_obs)[[1]] = dimnames(q_weir_sex_obs)[[1]] = dimnames(q_weir_origin_obs)[[1]] = dimnames(q_carc_age_obs)[[1]] = dimnames(q_carc_sex_obs)[[1]] = dimnames(q_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]

q_weir_new_obs = list(
  q_weir_age_obs = q_weir_age_obs,
  q_weir_sex_obs = q_weir_sex_obs,
  q_weir_origin_obs = q_weir_origin_obs
)

q_carc_new_obs = list(
  q_carc_age_obs = q_carc_age_obs,
  q_carc_sex_obs = q_carc_sex_obs,
  q_carc_origin_obs = q_carc_origin_obs
)

@@

```{r weir-comp-fit-funcs}

# for completely disaggregated fits
weir_comp_fit_plot = function(j) {
  # calculate observed q
  q_obs = t(apply(jags_data$weir_x_obs[,,j], 1, function(y) y/sum(y)))

@@

  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each age, aggregated across sexes and origins
weir_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,1,pop]$", pop = j)), q_weir_new_obs$q_weir_age_obs[observable,1,j], main = TeX("$Age\\,3$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,2,pop]$", pop = j)), q_weir_new_obs$q_weir_age_obs[observable,2,j], main = TeX("$Age\\,4$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,3,pop]$", pop = j)), q_weir_new_obs$q_weir_age_obs[observable,3,j], main = TeX("$Age\\,5$"), ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each sex, aggregated across ages and origins
weir_comp_fit_plot_sex = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,1,pop]$", pop = j)), q_weir_new_obs$q_weir_sex_obs[observable,1,j], main = TeX("$Females$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,2,pop]$", pop = j)), q_weir_new_obs$q_weir_sex_obs[observable,2,j], main = TeX("$Males$"), ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each origin, aggregated across ages and sexes
weir_comp_fit_plot_origin = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,1,pop]$", pop = j)), q_weir_new_obs$q_weir_origin_obs[observable,1,j], main = TeX("$NOR$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_origin[.+,2,pop]$", pop = j)), q_weir_new_obs$q_weir_origin_obs[observable,2,j], main = TeX("$HOR$"), ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}
```

#### By Age/Sex/Origin {.tabset .tabset-pills}

This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.

##### CAT

```{r cat-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_cat)
```

##### LOS

```{r los-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_los)
```

##### MIN

```{r min-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_min)
```

##### UGR

```{r ugr-weir-comp-fit, fig.width = 8, fig.height = 5}
weir_comp_fit_plot(j_ugr)
```

#### By Age {.tabset .tabset-pills}

These figures show the agreement of the model with the weir composition data by age, aggregated by sex and origin.

##### CAT

```{r cat-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_cat)
```

##### LOS

```{r los-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_los)
```

##### MIN

```{r min-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_min)
```

##### UGR

```{r ugr-weir-comp-fit-age, fig.width = 8, fig.height = 3.5}
weir_comp_fit_plot_age(j_ugr)
```

#### By Sex {.tabset .tabset-pills}

These figures show the agreement of the model with the weir composition data by sex, aggregated by age and origin.

##### CAT

```{r cat-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_sex(j_cat)
```

##### LOS

```{r los-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_sex(j_los)
```

##### MIN

```{r min-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_sex(j_min)
```

##### UGR

```{r ugr-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_sex(j_ugr)
```

#### By Origin {.tabset .tabset-pills}

These figures show the agreement of the model with the weir composition data by origin, aggregated by age and sex.

##### CAT

```{r cat-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_cat)
```

##### LOS

```{r los-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_los)
```

##### MIN

```{r min-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_min)
```

##### UGR

```{r ugr-weir-comp-fit-origin, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_origin(j_ugr)
```

@@

```{r carc-comp-fit-funcs}

# for completely disaggregated fits
carc_comp_fit_plot = function(j) {

@@

  par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,1,pop]$", pop = j)), q_obs[observable,1], main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,2,pop]$", pop = j)), q_obs[observable,2], main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,3,pop]$", pop = j)), q_obs[observable,3], main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,4,pop]$", pop = j)), q_obs[observable,4], main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,5,pop]$", pop = j)), q_obs[observable,5], main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,6,pop]$", pop = j)), q_obs[observable,6], main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,7,pop]$", pop = j)), q_obs[observable,7], main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,8,pop]$", pop = j)), q_obs[observable,8], main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,9,pop]$", pop = j)), q_obs[observable,9], main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,10,pop]$",pop = j)), q_obs[observable,10], main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,11,pop]$",pop = j)), q_obs[observable,11], main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj[.+,12,pop]$",pop = j)), q_obs[observable,12], main = TeX("$Male\\,Age\\,5\\,(HOR)$"))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
}

# for fits to each age, aggregated across sexes and origins
carc_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,1,pop]$", pop = j)), q_carc_new_obs$q_carc_age_obs[observable,1,j], main = TeX("$Age\\,3$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,2,pop]$", pop = j)), q_carc_new_obs$q_carc_age_obs[observable,2,j], main = TeX("$Age\\,4$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_age[.+,3,pop]$", pop = j)), q_carc_new_obs$q_carc_age_obs[observable,3,j], main = TeX("$Age\\,5$"))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each sex, aggregated across ages and origins
carc_comp_fit_plot_sex = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,1,pop]$", pop = j)), q_carc_new_obs$q_carc_sex_obs[observable,1,j], main = TeX("$Females$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_sex[.+,2,pop]$", pop = j)), q_carc_new_obs$q_carc_sex_obs[observable,2,j], main = TeX("$Males$"))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each origin, aggregated across ages and sexes
carc_comp_fit_plot_origin = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,1,pop]$", pop = j)), q_carc_new_obs$q_carc_origin_obs[observable,1,j], main = TeX("$NOR$"))
  plot_tseries(post_summ(post, sub_index("^q_Sa_adj_origin[.+,2,pop]$", pop = j)), q_carc_new_obs$q_carc_origin_obs[observable,2,j], main = TeX("$HOR$"))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

#### By Age/Sex/Origin {.tabset .tabset-pills}

This is the resolution the model fits to: each year slice is treated as a 12-element multinomial vector.

##### CAT

```{r cat-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_cat)
```

##### LOS

```{r los-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_los)
```

##### MIN

```{r min-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_min)
```

##### UGR

```{r ugr-carc-comp-fit, fig.width = 8, fig.height = 5}
carc_comp_fit_plot(j_ugr)
```

#### By Age {.tabset .tabset-pills}

These figures show the agreement of the model with the carcass composition data by age, aggregated by sex and origin.

##### CAT

```{r cat-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_cat)
```

##### LOS

```{r los-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_los)
```

##### MIN

```{r min-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_min)
```

##### UGR

```{r ugr-carc-comp-fit-age, fig.width = 8, fig.height = 3.5}
carc_comp_fit_plot_age(j_ugr)
```

#### By Sex {.tabset .tabset-pills}

These figures show the agreement of the model with the carcass composition data by sex, aggregated by age and origin.

##### CAT

```{r cat-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_sex(j_cat)
```

##### LOS

```{r los-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_sex(j_los)
```

##### MIN

```{r min-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_sex(j_min)
```

##### UGR

```{r ugr-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_sex(j_ugr)
```

#### By Origin {.tabset .tabset-pills}

These figures show the agreement of the model with the carcass composition data by origin, aggregated by age and sex.

##### CAT

```{r cat-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_cat)
```

##### LOS

```{r los-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_los)
```

##### MIN

```{r min-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_min)
```

##### UGR

```{r ugr-carc-comp-fit-origin, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_origin(j_ugr)
```
